\subsection{LSP-00-35: Linkage of catalog query results to related catalog data}
\label{lsp-00-35}

\subsubsection{Requirements}

???

\subsubsection{Test items}

This test will check for the ability, in the Portal Aspect of the LSST Science Platform, to match catalog data with related catalog data.  
Specifically, the test verifies the ability to navigate from a coadded source catalog entry to the associated forced photometry.


\subsubsection{Intercase dependencies}

This test case relies on multiple behaviors explored by other LSP-00-* test cases.


\subsubsection{Environmental needs}

The test must, and can only, be carried out on the PDAC instance of the Science Platform.

The test may be performed from any client computer on the public Internet.
The computer used, and the network connection involved, shall be documented in the test report.

The test requires access via the NCSA VPN from the client to the PDAC data services 
(which means that the performance of the VPN is a contributor to the performance observed).

The client computer must have an up-to-date mainstream Web browser, the identity of which shall be documented in the test report.


\subsubsection{Input specification}

The test requires the presence of the following SDSS data, from the Summer 2013 LSST processing, in the PDAC systems:

\begin{itemize}

  \item{The coadded source catalog; and}
  \item{The forced photometry catalog driven from the $i$-band coadded sources.}

\end{itemize}


\subsubsection{Output specification}

The output will consist of:

\begin{itemize}
  \item{A written log of the tests performed on the GUI-based Portal Aspect.}
\end{itemize}


\subsubsection{Procedure}

\begin{enumerate}

  \item{Log host and networking details of the client host to be used.
 Log the Web browser version to be used.}
  \item{Establish VPN connectivity to the PDAC at NCSA.}
  \item{Manually perform, and log, the following steps against the Portal Aspect:
    \begin{enumerate}
      \item{Navigate to the PDAC Portal.  Log the URL used to do so.}
      \item{Perform a catalog query against the i-band coadded source catalog within the Stripe 82 area.}
      \item{Request the time series from the forced photometry catalog for a selected source.}
      \item{Confirm that the data retrieved corresponds to the selected coadded source.}
      \item{Document the query results with screen shots.}
    \end{enumerate}
  }

\end{enumerate}
